Notes

### 2021-02-06 supCLT-ind.tex
add supCLT-ind.tex

@@

@@

@@

@@

	The following analytic result is elementary, and will also be used in the proof of Theorem \ref{thm: II}.
	\begin{lem}
\label{ineq: analysis}
	There exists a constant $C>0$, such that for any $x,y \in \mathbb R$,
\[
    |(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|
    \leq C(|x||y|^{\beta}+|x|^{\beta}|y|).
\]
\end{lem}
\begin{comment}
\begin{proof}
   	Note that
\[
  	\lim_{|y|\rightarrow \infty}\frac{(y+1)^{1+\beta}-y^{1+\beta}-1}{y^{\beta}}
  	=\lim_{|y|\rightarrow \infty}\frac{(y+1)^{1+\beta}-y^{1+\beta}}{y^{\beta}}
  	=\lim_{|y|\rightarrow \infty}\big((1+\frac{1}{y})^{1+\beta}-1\big)y = 1+\beta.
\]
	Using this and continuity, we get that there exists $C_1>0$ such that for all $|y|\geq 1$,
\[
  	|(1+y)^{1+\beta}-y^{1+\beta}-1|
  	\leq C_1 |y|^{\beta}.
\]
 	Note that if $x = 0$ or $y= 0$, then the desired result is trivial.
	So we only need to consider the case that $x \neq 0$ and $y \neq 0$.
 	In this case, if $|x|\geq |y|$, we have
\[
	|(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|
	\leq |y|^{1+\beta}\bigg(\Big|\Big(1+\frac{x}{y}\Big)^{1+\beta}-\Big(\frac{x}{y}\Big)^{1+\beta}-1\Big|\bigg)
	\leq C_1|y||x|^{\beta};
\]
	and  if $|x|\leq |y|$, we have
\[
	|(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|
	\leq |x|^{1+\beta}\bigg( \Big| \Big(1+\frac{y}{x}\Big)^{1+\beta}-\Big(\frac{y}{x}\Big)^{1+\beta}-1\Big|\bigg)
	\leq C_1|x||y|^{\beta}.
\]
	Combining the above, we immediately get the desired result.
\end{proof}
\end{comment}

@@

@@

>>>>

%{
{\bf Zhenyao: give definition for this non-integer power here.}
%}

@@

%{
{\bf ZS: page 4 line 1. I think that “$\leq$” should be “$>$”}
%}

@@

%{
{\bf ZS: add some comments about the second Assumption here about its limitation. Why we are not generalizing it to the slowly varying case.}
%}

@@

%{
{\bf ZS: Give the definition of $\mathcal P^+$ here.}
%}

@@

	The following analytic result is elementary, and will also be used in the proof of Theorem \ref{thm: II}.
\begin{lem} \label{ineq: analysis}
	There exists a constant $C>0$, such that for any $x,y \in \mathbb R$,
\[
    |(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|
    \leq C(|x||y|^{\beta}+|x|^{\beta}|y|).
\]
\end{lem}
%{
	{\bf ZS: Give the definition of $x^\beta$ for negative numbers.}
%}
\begin{comment}
\begin{proof}
   	Note that
\[
  	\lim_{|y|\rightarrow \infty}\frac{(y+1)^{1+\beta}-y^{1+\beta}-1}{y^{\beta}}
  	=\lim_{|y|\rightarrow \infty}\frac{(y+1)^{1+\beta}-y^{1+\beta}}{y^{\beta}}
  	=\lim_{|y|\rightarrow \infty}\big((1+\frac{1}{y})^{1+\beta}-1\big)y = 1+\beta.
\]
	Using this and continuity, we get that there exists $C_1>0$ such that for all $|y|\geq 1$,
\[
  	|(1+y)^{1+\beta}-y^{1+\beta}-1|
  	\leq C_1 |y|^{\beta}.
\]
 	Note that if $x = 0$ or $y= 0$, then the desired result is trivial.
	So we only need to consider the case that $x \neq 0$ and $y \neq 0$.
 	In this case, if $|x|\geq |y|$, we have
\[
	|(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|
	\leq |y|^{1+\beta}\bigg(\Big|\Big(1+\frac{x}{y}\Big)^{1+\beta}-\Big(\frac{x}{y}\Big)^{1+\beta}-1\Big|\bigg)
	\leq C_1|y||x|^{\beta};
\]
	and  if $|x|\leq |y|$, we have
\[
	|(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|
	\leq |x|^{1+\beta}\bigg( \Big| \Big(1+\frac{y}{x}\Big)^{1+\beta}-\Big(\frac{y}{x}\Big)^{1+\beta}-1\Big|\bigg)
	\leq C_1|x||y|^{\beta}.
\]
	Combining the above, we immediately get the desired result.
\end{proof}
\end{comment}

@@

%{
{\bf ZS: In the second line of (2.9), change ’$T_uf$’ into ’$T_uf_s$’.}
%}

@@

%{
{\bf ZS: there is a $1/t$ missed in the above inequality.}
%}
